---
title: "AN588-Week-3-chuhan"
author: "Lia"
date: "2023-09-29"
output:
  prettydoc::html_pretty:
  theme: cayman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1

What is the probablity that she will hear more than 8 calls during any given session? 

```{r}
l <- 15
Pr8 <- ppois(8, l, lower.tail = FALSE)
Pr8
```

Question 1 complete :)

## Question 2

What is the probablity that she will hear no calls in a session? 
```{r}
Pr0 <- ((l^0)*exp(-l))/(factorial(0))
Pr0
```

Question 2 complete :)

## Question 3

What is the probability that she will hear exactly 3 calls in a session? 

```{r}
Pr3 <- ((l^3)*exp(-l))/(factorial(3))
Pr3
```

Question 3 complete :)

## Question 4

Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.

```{r}
x <- 0:30
CallPr <- dpois(x=x, lambda=l)
barplot(CallPr, names.arg=x, space=0, xlab="Titis Calls", ylab="Probability of Call Number", main="Probability Mass Function of Titis Calls")
```

Question 4 complete :)

## Question 5

Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions).

```{r}
nSat <- 104
SimResult <- rpois(nSat, l)
SimResult
```

Question 5 complete :)

## Question 6

Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above?

```{r}
hist(SimResult, breaks=seq(from=0, to=30, by=1), probability=TRUE, main="Titis Call 2 Year Simulation", xlab="Number of Calls", ylab = "Probability of Call Number", xlim=c(0,30))
```

**Note: **I noticed that the hist() plot changes every time the Rmd file is knitted as Question 5 produces different simulation results. Is there a way or is it necessary to make the simulation result fixed? 

Anyway, question 6 complete :)

***

Homework 2 complete :D